---
title: "Hollyer Replication"
output: html_document
date: "2023-03-16"
---


```{r Setup}
library(Hmisc)
r = function(x) round(x, digits=3)
library(rdrobust)
library(readstata13)
library(ggplot2)
library(rdd)
library(tidyverse)
library(rddensity)
setwd("C:/Users/edmun/Documents/2022-2023 - MSc Politics Research/97 - Replication Game/Hollyer Replication")
data = read.dta13("./brazil-RD-data.dta")
names(data)

cross_national = read.dta13("./cross-national-data.dta")
```

```{r Table 2 Original}


# ----------------------------- #
# Now put results into a table to print to latex
# ----------------------------- #
outnm = c("Young", "Young and Outsider") 
outvar = cbind(data$youngF_inc_for1, data$outyg1F_inc_for1)

samplenm = c("Opn")
samplevar = (data$dlameduck_runs==0)

colnms = c("Outcome","Sample", "Effect", "Robust p-value",  "Robust 95 CI", "Bandwidth (h)", "Bandwidth (b)", "N right", "N left")
res = matrix(data=NA, nrow=length(outnm), ncol=length(colnms), dimnames = list(NULL, colnms))

# default rdrobust
for(k in 1:length(outnm)) {
    cat("Analyzing outcome ", outnm[k], " sample ", samplenm, "\n")
    i = k
    
    indx = samplevar
    y = outvar[indx,k]
    x = data$mv_incparty[indx]
    
    rr = rdrobust(y=y, x=x)
    
    res[i,"Outcome"]        = outnm[k]
    res[i, "Sample"]        = samplenm
    res[i,"Effect"]         = r(rr$Estimate[1])
    res[i,"Robust p-value"] = r(rr$pv[3])
    res[i,"Robust 95 CI"]   = paste("[", r(rr$ci["Robust",1]), ",",  r(rr$ci["Robust",2]), "]", sep="")
    res[i,"Bandwidth (h)"]  = r(rr$bws["h",1])
    res[i,"Bandwidth (b)"]  = r(rr$bws["b",1])
    res[i,"N right"]        = rr$N_h[1]
    res[i,"N left"]         = rr$N_h[2]
}

res.hb = res

# rdrobust with rho=1
res = matrix(data=NA, nrow=length(outnm), ncol=length(colnms), dimnames = list(NULL, colnms))

for(k in 1:length(outnm)) {
    cat("Analyzing outcome ", outnm[k], " sample ", samplenm, "\n")
    i = k
    
    indx = samplevar
    y = outvar[indx,k]
    x = data$mv_incparty[indx]
    
    rr = rdrobust(y=y, x=x, rho=1)
    
    res[i,"Outcome"]        = outnm[k]
    res[i, "Sample"]        = samplenm
    res[i,"Effect"]         = r(rr$Estimate[1])
    res[i,"Robust p-value"] = r(rr$pv[3])
    res[i,"Robust 95 CI"]   = paste("[", r(rr$ci["Robust",1]), ",",  r(rr$ci["Robust",2]), "]", sep="")
    res[i,"Bandwidth (h)"]  = r(rr$bws["h",1])
    res[i,"Bandwidth (b)"]  = r(rr$bws["b",1])
    res[i,"N right"]        = rr$N_h[1]
    res[i,"N left"]         = rr$N_h[2]
    
}

res.rho1 = res

# Default rdrobust specs
print(res.hb)
# Using h=b (rho=1)
print(res.rho1)


# Make table pretty and print
# Young and Young outsider for Open seat sample only
tab = rbind(res.hb[,c(-2)])
colnames(tab)[2] = "$\\tau^\\mathtt{RD}$"
colnames(tab)[3] = "$\\mathtt{p}$-$\\mathtt{value}$"
colnames(tab)[4] = "$\\mathtt{95\\%\\;CI}$"
colnames(tab)[5] = "$\\mathtt{h}$"
colnames(tab)[6] = "$\\mathtt{b}$"
colnames(tab)[7] = "$\\mathtt{N}_{+}$"
colnames(tab)[8] = "$\\mathtt{N}_{-}$"
# Add confidence interval for rho=1
tab = cbind(tab,res.rho1[,"Robust 95 CI"])
colnames(tab)[9] = "$\\mathtt{95\\%\\;CI\\; (h=b)}$"
print(tab)

h.y  = res.hb[1,6]
b.y  = res.hb[1,7]
t.y  = res.hb[1,3]
ci.y=  res.hb[1,5]


h.yo  = res.hb[2,6]
b.yo  = res.hb[2,7]
t.yo  = res.hb[2,3]
ci.yo=  res.hb[2,5]

```

```{r Figure 6 Original}

##----------------------------#
# youngF_inc_for1: Young indicator (35 or less)
##----------------------------#
outnm = "young"
y = data$youngF_inc_for1
x = data$mv_incparty
indx = (data$dlameduck_runs==0)

xpos = -25
ypos = 0.5
# only munis where lame-duck does *not* run 
g = rdplot(y[indx], x[indx], subset = (abs(x[indx]) <= 50), p=2,
       x.label="Incumbent party's margin of victory at t", y.label = "Incumbent party's candidate at t+1 young indicator (original report)", title="")
annotation = data.frame( 
  x = c(xpos, xpos, xpos, xpos),
  y = c(ypos, ypos-0.03, ypos-0.06, ypos-0.09),
  label = c(paste("Local linear RD effect = ",t.y,sep=""), paste("Robust 95% CI = ",ci.y,sep=""), paste("Main bandwidth = ", h.y, sep=""),
            paste("Bias bandwidth = ", b.y, sep=""))
)
g$rdplot +  theme(axis.text=element_text(size=10),axis.title = element_text(size=15))

##----------------------------#
# outyg1F_inc_for1: Young outsider indicator (==0 is reserved for age>=35 and elected officials and government employees excluding military and police)
##----------------------------#

outnm = "out1young"
y=data$outyg1F_inc_for1
x = data$mv_incparty
indx = (data$dlameduck_runs==0)

# only munis where lame-duck does *not* run 
g = rdplot(y[indx], x[indx], subset = (abs(x[indx]) <= 50), p=2,
           x.label="Incumbent party's margin of victory at t", y.label = "Incumbent party's candidate at t+1 young and outsider", title="")
annotation = data.frame( 
  x = c(xpos, xpos, xpos, xpos),
  y = c(ypos, ypos-0.03, ypos-0.06, ypos-0.09),
  label = c(paste("Local linear RD effect = ",t.yo,sep=""), paste("Robust 95% CI = ",ci.yo,sep=""), paste("Main bandwidth = ", h.yo, sep=""),
            paste("Bias bandwidth = ", b.yo, sep=""))
)
g$rdplot + theme(axis.text=element_text(size=10), axis.title = element_text(size=15))

```

```{r Table E3 Original}

validation = read.dta13("./brazil-validation-data.dta")
dim(data)

outnm = c("Young Indicator", "Young and Outsider Indicator")
outvar = cbind(data$cand_youngF, data$cand_outyg1F)

colnms = c("Outcome", "Mean (I==1)", "Mean (I==0)",  "p-value", "N (I==1)", "N (I==0)")
res = matrix(data=NA, nrow=length(outnm), ncol=length(colnms), dimnames = list(NULL, colnms))

for(i in 1:length(outnm)) {
  cat("Analyzing outcome ", outnm[i], "\n")
  y = outvar[,i]
  x = data$err_mvparty
  
  rr = t.test(x[y==1],  x[y==0])
  
  res[i,"Outcome"]        = outnm[i]
  res[i,"Mean (I==1)"]    = r(mean(x[y==1], na.rm=T))
  res[i,"Mean (I==0)"]    = r(mean(x[y==0], na.rm=T))
  res[i,"p-value"]        = r(rr$p.value)
  res[i,"N (I==1)"]       = sum(!is.na(x[y==1]))
  res[i,"N (I==0)"]       = sum(!is.na(x[y==0]))
}
print(res)

# Make table pretty and print
# Young and Young outsider for Open seat sample only
tab = res[1:2,]
colnames(tab)[2] = "$\\mathtt{Mean}_1$"
colnames(tab)[3] = "$\\mathtt{Mean}_0$"
colnames(tab)[4] = "$\\mathtt{p}$-$\\mathtt{value}$"
colnames(tab)[5] = "$\\mathtt{N}_1$"
colnames(tab)[6] = "$\\mathtt{N}_0$"
tab[1,1] = "Margin of victory: young vs. not"
tab[2,1] = "Margin of victory: young \\& outsider vs. not"
print(tab)

```

```{r Figure 6 Replication}

data_noducks = data[data$dlameduck_runs == 0, ]

#Replication of Figure 6

rdplot(data_noducks$youngF_inc_for1, 
       data_noducks$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data_noducks$mv_incparty)<50, 
       p = 2)

rdplot(data_noducks$outyg1F_inc_for1, 
       data_noducks$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data_noducks$mv_incparty)<50, 
       p = 2)

#Polynomial 1

rdplot(data_noducks$youngF_inc_for1, 
       data_noducks$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data_noducks$mv_incparty)<50, 
       p = 1)

rdplot(data_noducks$outyg1F_inc_for1, 
       data_noducks$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data_noducks$mv_incparty)<50, 
       p = 1)

#Changing no. of bins

rdplot(data_noducks$youngF_inc_for1, 
       data_noducks$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data_noducks$mv_incparty)<50, 
       p = 2, nbins = nrow(data_noducks))

rdplot(data_noducks$outyg1F_inc_for1, 
       data_noducks$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data_noducks$mv_incparty)<50, 
       p = 2, nbins  = nrow(data_noducks))

```

```{r Figure 6 Full Sample}

#Replication of Figure 6

rdplot(data$youngF_inc_for1, 
       data$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data$mv_incparty)<50, 
       p = 2)

rdplot(data$outyg1F_inc_for1, 
       data$mv_incparty, c = 0, ci = FALSE, 
       binselect = "esmv", 
       subset = abs(data$mv_incparty)<50, 
       p = 2)

```


```{r Table 2 Replication - Young Candidate}

robust_young = rdrobust(data_noducks$youngF_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd")
summary(robust_young)

robust_young_hb = rdrobust(data_noducks$youngF_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", rho = 1)
summary(robust_young_hb)

```

```{r Table 2 Replication - Outsider Candidate}

robust_outsider = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd")
summary(robust_outsider)

robust_outsider_hb = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", rho = 1)
summary(robust_outsider)
```

```{r Table 2 Quadratic - Young Candidate}

q_young = rdrobust(data_noducks$youngF_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", p=2)
summary(q_young)

q_young_hb = rdrobust(data_noducks$youngF_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", rho = 1, p=2)
summary(q_young_hb)

```

```{r Table 2 Quadratic - Outsider Candidate}

q_outsider = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", p=2)
summary(linear_outsider)

q_outsider_hb = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", rho = 1, p=2)
summary(q_outsider_hb)
```

```{r Table 2 Bandwidth Selection Procedures}

msetwo_young = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "msetwo")

msetwo_young = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "msetwo")

summary(robust_twobandwidth_outsider)

summary(robust_twobandwidth_young)

msesum_young = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "msesum")

msesum_outsider = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "msesum")

summary(msesum_young)

summary(robust_twobandwidth_young)

```

```{r Table 2 Kernels}

kernel_young = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", 
                                     kernel = "uniform")

kernel_outsider = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", 
                                        kernel = "uniform")

summary(kernel_young)

summary(kernel_outsider)

triangle_young = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", 
                                     kernel = "triangular")

triangle_outsider = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", 
                                        kernel = "triangular")

summary(triangle_young)

summary(triangle_outsider)

ep_young = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", 
                                     kernel = "epanechnikov")

ep_outsider = rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, bwselect = "mserd", 
                                        kernel = "epanechnikov")

summary(ep_young)

summary(ep_outsider)

```

```{r Descriptives for running variable}

data_noducks %>% 
  ggplot(aes(x = mv_incparty)) + 
  geom_histogram(binwidth = 5) + 
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 20) + 
  geom_vline(xintercept = -20)

```

```{r Table 2 Bandwidth Selection - Young Candidate}

bandwidth <- seq(from = 5, to = 100, by = 5)  

coefficient <- NA 
se <- NA
obs <- NA
bw <- NA
ci_u <- NA
ci_l <- NA

# create a data.frame with all variables you want to incldue in your dataset
data_extract <- data.frame(bandwidth, coefficient, se, obs, bw, ci_u, ci_l)

# create a loop for each bandwidth that is indicated by 'i'
for(i in bandwidth){
 rdbw <- rdrobust(data_noducks$youngF_inc_for1, data_noducks$mv_incparty, c = 0, h=i) # run the model
                                      
# extract the model output (make sure to extract *robust* statistics)
data_extract$coefficient[data_extract$bandwidth==i]  <- rdbw$coef[3] 
data_extract$se[data_extract$bandwidth==i]  <- rdbw$se[3]
data_extract$obs[data_extract$bandwidth==i]  <- (rdbw$N_h[1] + rdbw$N_h[2]) 
data_extract$bw[data_extract$bandwidth==i]  <- (rdbw$bws[1, 1]) 
data_extract$ci_l[data_extract$bandwidth==i]  <- rdbw$ci[3,1]
data_extract$ci_u[data_extract$bandwidth==i]  <- rdbw$ci[3,2]
                   }

# Make sure the coefficient (and all other values) are numeric
data_extract$coefficient  <- as.numeric(data_extract$coefficient)

# Plot the estimates across bandwidths
ggplot(data = data_extract,
       aes(x = bandwidth, y = coefficient)) +
  geom_point(size = 0.8) +
  geom_ribbon(aes(ymin = ci_l, ymax = ci_u), alpha = 0.2) +
  geom_hline(aes(yintercept = 0), col = "red", linetype = 2) +
  coord_cartesian(ylim = c(-0.25, 0)) +
  theme_minimal() +
  labs(y = "LATE at Discontinuity", x = "Bandwidths (Vote Margin)")

```

```{r Table 2 Bandwidth Selection - Outsider Candidate}

bandwidth <- seq(from = 5, to = 100, by = 5)  

coefficient <- NA 
se <- NA
obs <- NA
bw <- NA
ci_u <- NA
ci_l <- NA

# create a data.frame with all variables you want to incldue in your dataset
data_extract <- data.frame(bandwidth, coefficient, se, obs, bw, ci_u, ci_l)

# create a loop for each bandwidth that is indicated by 'i'
for(i in bandwidth){
 rdbw <- rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = 0, h=i) # run the model
                                      
# extract the model output (make sure to extract *robust* statistics)
data_extract$coefficient[data_extract$bandwidth==i]  <- rdbw$coef[3] 
data_extract$se[data_extract$bandwidth==i]  <- rdbw$se[3]
data_extract$obs[data_extract$bandwidth==i]  <- (rdbw$N_h[1] + rdbw$N_h[2]) 
data_extract$bw[data_extract$bandwidth==i]  <- (rdbw$bws[1, 1]) 
data_extract$ci_l[data_extract$bandwidth==i]  <- rdbw$ci[3,1]
data_extract$ci_u[data_extract$bandwidth==i]  <- rdbw$ci[3,2]
                   }

# Make sure the coefficient (and all other values) are numeric
data_extract$coefficient  <- as.numeric(data_extract$coefficient)

# Plot the estimates across bandwidths
ggplot(data = data_extract,
       aes(x = bandwidth, y = coefficient)) +
  geom_point(size = 0.8) +
  geom_ribbon(aes(ymin = ci_l, ymax = ci_u), alpha = 0.2) +
  geom_hline(aes(yintercept = 0), col = "red", linetype = 2) +
  coord_cartesian(ylim = c(-0.25, 0)) +
  theme_minimal() +
  labs(y = "LATE at Discontinuity", x = "Bandwidths (Vote Margin)")

```

```{r Density Tests}

DCdensity(data_noducks$mv_incparty, cutpoint = 0, plot= TRUE, ext.out = TRUE)

title(xlab = "Winning Margin", ylab = "Density") # add labels
abline(v = 0, lty = 1) # add a vertical line at x = 0


rdd <- rddensity(data_noducks$mv_incparty, c = 0)
summary(rdd)

plot_rdd <- rdplotdensity(rdd, data_noducks$mv_incparty, plotRange = c(-50, 50), CIuniform = TRUE)


```

```{r Table 2 Placebo Cutoffs - Young Candidate}

cutoff <- seq(from = -10, to = 10, by = 1)  

coefficient <- NA 
se <- NA
obs <- NA
bw <- NA
ci_u <- NA
ci_l <- NA

# create a data.frame with all variables you want to incldue in your dataset
data_extract <- data.frame(cutoff, coefficient, se, obs, bw, ci_u, ci_l)

# create a loop for each bandwidth that is indicated by 'i'
for(i in cutoff){
 rdbw <- rdrobust(data_noducks$youngF_inc_for1, data_noducks$mv_incparty, c = i, bwselect="mserd") # run the model
                                      
# extract the model output (make sure to extract *robust* statistics)
data_extract$coefficient[data_extract$cutoff==i]  <- rdbw$coef[3] 
data_extract$se[data_extract$cutoff==i]  <- rdbw$se[3]
data_extract$obs[data_extract$cutoff==i]  <- (rdbw$N_h[1] + rdbw$N_h[2]) 
data_extract$bw[data_extract$cutoff==i]  <- (rdbw$bws[1, 1]) 
data_extract$ci_l[data_extract$cutoff==i]  <- rdbw$ci[3,1]
data_extract$ci_u[data_extract$cutoff==i]  <- rdbw$ci[3,2]
                   }

# Make sure the coefficient (and all other values) are numeric
data_extract$coefficient  <- as.numeric(data_extract$coefficient)

# Plot the estimates across bandwidths
ggplot(data = data_extract,
       aes(x = cutoff, y = coefficient)) +
  geom_point(size = 0.8) +
  geom_ribbon(aes(ymin = ci_l, ymax = ci_u), alpha = 0.2) +
  geom_hline(aes(yintercept = 0), col = "red", linetype = 2) +
  coord_cartesian(ylim = c(-0.25, 0)) +
  theme_minimal() +
  labs(y = "LATE at Discontinuity", x = "cutoff (Vote Margin)")

```

```{r Table 2 Placebo Cutoffs - Young Candidate}

cutoff <- seq(from = -10, to = 10, by = 1)  

coefficient <- NA 
se <- NA
obs <- NA
bw <- NA
ci_u <- NA
ci_l <- NA

# create a data.frame with all variables you want to incldue in your dataset
data_extract <- data.frame(cutoff, coefficient, se, obs, bw, ci_u, ci_l)

# create a loop for each bandwidth that is indicated by 'i'
for(i in cutoff){
 rdbw <- rdrobust(data_noducks$outyg1F_inc_for1, data_noducks$mv_incparty, c = i, bwselect="mserd") # run the model
                                      
# extract the model output (make sure to extract *robust* statistics)
data_extract$coefficient[data_extract$cutoff==i]  <- rdbw$coef[3] 
data_extract$se[data_extract$cutoff==i]  <- rdbw$se[3]
data_extract$obs[data_extract$cutoff==i]  <- (rdbw$N_h[1] + rdbw$N_h[2]) 
data_extract$bw[data_extract$cutoff==i]  <- (rdbw$bws[1, 1]) 
data_extract$ci_l[data_extract$cutoff==i]  <- rdbw$ci[3,1]
data_extract$ci_u[data_extract$cutoff==i]  <- rdbw$ci[3,2]
                   }

# Make sure the coefficient (and all other values) are numeric
data_extract$coefficient  <- as.numeric(data_extract$coefficient)

# Plot the estimates across bandwidths
ggplot(data = data_extract,
       aes(x = cutoff, y = coefficient)) +
  geom_point(size = 0.8) +
  geom_ribbon(aes(ymin = ci_l, ymax = ci_u), alpha = 0.2) +
  geom_hline(aes(yintercept = 0), col = "red", linetype = 2) +
  coord_cartesian(ylim = c(-0.25, 0)) +
  theme_minimal() +
  labs(y = "LATE at Discontinuity", x = "cutoff (Vote Margin)")

```


#Notes:

1. They don't do much/any robustness on the RD model - they refer to the previous paper (Klasnja and Tituinik 2017), but that paper used a different dependent variable.

2. They validate the measures but don't provide the code - just the prediction errors. They reference machine learning but they don't provide the code. 

3. The formal model seems fine. 

4. Cross national and RDD - set tasks. 